After identifying potential investments, asset managers face the question about how to allocate the limited resources they have to each of them taking into account the particular constrains and goals of their investors. This task is of great importance for the asset managers' mandate to generate high risk-adjusted returns. Harry M. Markowitz was the first to develop and present a systematic approach to this asset allocation problem in 1952, earning him a Nobel Memorial Prize in Economic Sciences in 1990 \cite{markowitznobelprize}. However, Markowitz's portfolio construction model suffers from some pitfalls in practical implementations that limit its performance out-of-sample. DeMiguel et al. \cite{equalweight} show that portfolios generated using naive methods like equal weight or inverse variance allocation can even out-perform Markowitz's optimal portfolios.

Michaud and Michaud \cite{michaudreturnsstability} argue that portfolios constructed using Markowitz's model are prone to be unstable, which results in high transactions costs each time it has to be re-balanced, and also tend to be concentrated into a reduced number of assets.

Ledoit and Wolf \cite{ledoit} present a method, called covariance shrinkage, to replace the sample covariance matrix as input for Markowitz's portfolio optimisation model, because the claim that the sample covariance matrix contains too much noise. Their method relies on using a structured estimator, called shrinkage target, to transform the sample covariance matrix into a matrix with less noise.

De Nard \cite{denard} goes further that Ledoit and Wolf to define a covariance matrix shrinkage method that takes into account the idiosyncratic differences between some of the assets available in the portfolio optimisation process. In his method, assets are first clustered into groups with similar characteristics to then apply the covariance shrinkage method to each of the groups separately.

Finally, López de Prado \cite{lopezmain} provides a new portfolio optimisation method that tries to tackle the instability of Markowitz's optimal portfolios by introducing the concept of hierarchy among the portfolio assets. He claims that his method, called hierarchical risk parity, not only reduces portfolio instability, but also concentration and it even improves portfolio performance out-of-sample.

We analyse Markowitz's Portfolio Construction and its pitfalls to discuss the source of instability, specially what López de Prado calls \textit{Markowitz's Curse}. Moreover, we present the two approaches to improve stability via covariance matrix shrinkage introduced by Ledoit and Wolf and De Nard. Finally, we describe López de Prado's hierarchical risk parity method. We compare the results of all these optimisation methods with respect to stability (average portfolio turnover), concentration (normalised Herfindahl-Hirsch-Index) and risk-adjusted performance (annualised Sharpe Ratio) on the basis of multi-asset portfolios with the help of ETFs. The details of the practical implementation framework can be found in appendix \ref{appendix:PracticalImplementationFramework}.

Apart from this introduction, this bachelor thesis consist of 3 sections which are briefly described in the following paragraphs.

In section \ref{section:TheAssetAllocationProblem} we give a brief introduction to the problem of finding the optimal portfolio for an investor and define 2 naive portfolio allocation models and Markowitz's portfolio allocation model. Moreover, we also analyse the practical results of Markowitz's optimal portfolios and the source of their instability.

In section \ref{section:ImprovingMarkowitzsPortfolioOptimisationModel}, we define and discuss the 2 covariance shrinkage methods and the method proposed by López de Prado, and compare their practical implementation results to the Markowitz's optimal portfolios from section \ref{section:TheAssetAllocationProblem}.

Finally, in section \ref{section:Conclusion}, we conclude that the sensitivity to the input covariance matrix' condition number in the computation of Markowitz's minimum volatility portfolios is highly relevant and cannot be ignored. The covariance shrinkage methods described in this thesis can help reduce the condition number of the input covariance matrix and its consequences. Moreover, alternative asset allocation models, like the hierarchical risk parity method, as well as naive models, like equal weight and inverse variance allocation, can be good substitutes for Markowitz's minimum volatility portfolios, even if they aren't optimal in-sample.