\subsection*{Equity ETPs}
    % Equity alphabetically sorted.
    \begin{itemize}
        \item iShares Global Industrials ETF with ticker "EXI" which seeks to track the investment results of an index composed of global equities in the industrials sector. More specifically, the index tracked is the S{\&}P Global 1200 Industrials Sector Index (TM). The top sub-sectors represented in the ETF holdings are capital goods, transportation and commercial and professional services. Source: \href{https://www.ishares.com/us/literature/fact-sheet/exi-ishares-global-industrials-etf-fund-fact-sheet-en-us.pdf}{iShares Global Industrials ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_exi}.
        
        \item iShares MSCI Global Energy Producers ETF with ticker "FILL" which seeks to track the investment results of an index composed of global equities of companies primarily engaged in the business of energy exploration and production. More specifically, the index tracked is the MSCI ACWI Select Energy Producers Investable Market Index. The top sub-sectors represented in the ETF holdings are integrated oil and gas, oil and gas exploration and production, oil and gas refining and marketing and transportation, coal and consumable fuels and oil and gas drilling. Source: \href{https://www.ishares.com/us/literature/fact-sheet/fill-ishares-msci-global-energy-producers-etf-fund-fact-sheet-en-us.pdf}{iShares MSCI Global Energy Producers ETF Fact Sheet as of June 30, 2021}. % \cite{factsheet_fill}.
        
        \item iShares Global Infrastructure ETF with ticker "IGF" which seeks to track the investment results of an index composed of developed market equities in the infrastructure industry. More specifically, the index tracked is the S{\&}P Global Infrastructure Index. The top sub-sectors represented in the ETF holdings are utilities, transportation and energy. Source: \href{https://www.ishares.com/us/literature/fact-sheet/igf-ishares-global-infrastructure-etf-fund-fact-sheet-en-us.pdf}{iShares Global Infrastructure ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_igf}.
        
        \item iShares Global Financials ETF with ticker "IXG" which seeks to track the investment results of an index composed of global equities in the financials sector. More specifically, the index tracked is the S{\&}P Global 1200 Financials Sector Index (TM). The top sub-sectors represented in the ETF holdings are banks, diversified financials and insurance. Source: \href{https://www.ishares.com/us/literature/fact-sheet/ixg-ishares-global-financials-etf-fund-fact-sheet-en-us.pdf}{iShares Global Financials ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_ixg}.
        
        \item iShares Global Healthcare ETF with ticker "IXJ" which seeks to track the investment results of an index composed of global equities in the healthcare sector. More specifically, the index tracked is the S{\&}P Global 1200 Healthcare Sector Index (TM). The top sub-sectors represented in the ETF holdings are pharmaceuticals, biotech and life sciences and health care equipment and services. Source: \href{https://www.ishares.com/us/literature/fact-sheet/ixj-ishares-global-healthcare-etf-fund-fact-sheet-en-us.pdf}{iShares Global Healthcare ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_ixj}.
        
        \item iShares Global Tech ETF with ticker "IXN" which seeks to track the investment results of an index composed of global equities in the technology sector. More specifically, the index tracked is the S{\&}P Global 1200 Information Technology Sector Index (TM). The top sub-sectors represented in the ETF holdings are software and services, tech hardware and equipment, semiconductors and semiconductor equipment. Source: \href{https://www.ishares.com/us/literature/fact-sheet/ixn-ishares-global-tech-etf-fund-fact-sheet-en-us.pdf}{iShares Global Tech ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_ixn}.
        
        \item iShares Global Comm Services ETF with ticker "IXP" which seeks to track the investment results of an index composed of global equities in the communication services sector. More specifically, the index tracked is the S{\&}P Global 1200 Communication Services 4.5/22.5/45 Capped Index. The top sub-sectors represented in the ETF holdings are interactive media and services, integrated telecommunication services, movies and entertainment, cable and satellite and wireless telecommunication services. Source: \href{https://www.ishares.com/us/literature/fact-sheet/ixp-ishares-global-comm-services-etf-fund-fact-sheet-en-us.pdf}{iShares Global Comm Services ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_ixp}.
        
        \item iShares Global Utilities ETF with ticker "JXI" which seeks to track the investment results of an index composed of global equities in the utilities sector. More specifically, the index tracked is the S{\&}P Global 1200 Utilities (Sector) Capped Index. The top sub-sectors represented in the ETF holdings are electric utilities, multi-utilities, gas utilities and water utilities. Source: \href{https://www.ishares.com/us/literature/fact-sheet/jxi-ishares-global-utilities-etf-fund-fact-sheet-en-us.pdf}{iShares Global Utilities ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_jxi}.
        
        \item iShares Global Consumer Staples ETF with ticker "KXI" which seeks to track the investment results of an index composed of global equities in the consumer staples sector. More specifically, the index tracked is the S{\&}P Global 1200 Consumer Staples Sector Capped Index. The top sub-sectors represented in the ETF holdings are food, beverages and tobacco, household and personal products and food and staples retailing. Source: \href{https://www.ishares.com/us/literature/fact-sheet/kxi-ishares-global-consumer-staples-etf-fund-fact-sheet-en-us.pdf}{iShares Global Consumer Staples ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_kxi}.
        
        \item iShares Global Materials ETF with ticker "MXI" which seeks to track the investment results of an index composed of global equities in the materials sector. More specifically, the index tracked is the S{\&}P Global 1200 Materials Sector Index (TM). The top sub-sectors represented in the ETF holdings are chemicals, metals and mining, construction materials and containers and packaging. Source: \href{https://www.ishares.com/us/literature/fact-sheet/mxi-ishares-global-materials-etf-fund-fact-sheet-en-us.pdf}{iShares Global Materials ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_mxi}.
       
        % Real estate ETF!
        \item iShares Global REIT ETF with ticker "REET" which seeks to track the investment results of an index composed of global real estate equities in developed and emerging markets. More specifically, the index tracked is the FTSE EPRA Nareit Global REITS Net Total Return Index. The top sub-sectors represented in the ETF holdings are retail REIT's, industrial REIT's, residential REIT's and specialised REIT's. Source: \href{https://www.ishares.com/us/literature/fact-sheet/reet-ishares-global-reit-etf-fund-fact-sheet-en-us.pdf}{iShares Global REIT ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_reet}. This single equity ETF is used as a proxy to represent the real estate asset class.
        
        \item iShares Global Consumer Discretionary ETF with ticker "RXI" which seeks to track the investment results of an index composed of global equities in the consumer discretionary sector. More specifically, the index tracked is the S{\&}P Global 1200 Consumer Discretionary Sector Capped Index. The top sub-sectors represented in the ETF holdings are retailing, autos and components, consumer durables and consumer services. Source: \href{https://www.ishares.com/us/literature/fact-sheet/rxi-ishares-global-consumer-discretionary-etf-fund-fact-sheet-en-us.pdf}{iShares Global Consumer Discretionary ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_rxi}.
    \end{itemize}
    
\subsection*{Fixed Income ETPs}
    % Fixed income alphabetically sorted.
    \begin{itemize}
        \item iShares Core International Aggregate Bond ETF with ticker "IAGG" which seeks to track the investment results of an index composed of global non-U.S. dollar-denominated investment-grade bonds that mitigates exposure to fluctuations between the value of the component currencies and the U.S. dollar. More specifically, the index tracked is the Bloomberg Barclays Global Aggregate ex USD 10\% Issuer Capped (Hedged) Index. Most of the ETF holdings are rated single A or higher, and have maturities between 3 and 10 years. Source: \href{https://www.ishares.com/us/literature/fact-sheet/iagg-ishares-core-international-aggregate-bond-etf-fund-fact-sheet-en-us.pdf}{iShares Core International Aggregate Bond ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_iagg}.
        
        \item iShares Core 10+ Year USD Bond ETF with ticker "ILTB" which seeks to track the investment results of an index composed of U.S. dollar-denominated bonds that are rated either investment-grade or high-yield with remaining maturities greater than 10 years. More specifically, the index tracked is the Bloomberg Barclays U.S. Universal 10+ Year Index. Most of the ETF holdings are rated AAA or BBB. Source: \href{https://www.ishares.com/us/literature/fact-sheet/iltb-ishares-core-10-year-usd-bond-etf-fund-fact-sheet-en-us.pdf}{iShares Core 10+ Year USD Bond ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_iltb}.
        
        \item iShares Core 5-10 Year USD Bond ETF with ticker "IMTB" which seeks to track the investment results of an index composed of U.S. dollar-denominated bonds that are rated either investment-grade or high-yield with remaining effective maturities between 5 and 10 years. More specifically, the index tracked is the Bloomberg US Universal 5-10 Years Index. Most of the ETF holdings are rated AAA. Source: \href{https://www.ishares.com/us/literature/fact-sheet/imtb-ishares-core-5-10-year-usd-bond-etf-fund-fact-sheet-en-us.pdf}{iShares Core 5-10 Year USD Bond ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_imtb}.
        
        \item iShares Core 1-5 Year USD Bond ETF with ticker "ISTB" which seeks to track the investment results of an index composed of U.S. dollar-denominated bonds that are rated either investment-grade or high-yield with remaining maturities between 1 and 5 years. Most of the ETF holdings are rated AAA. Source: \href{https://www.ishares.com/us/literature/fact-sheet/istb-ishares-core-1-5-year-usd-bond-etf-fund-fact-sheet-en-us.pdf}{iShares Core 1-5 Year USD Bond ETF Fact Sheet as of June 30, 2021}.% \cite{factsheet_istb}.
    \end{itemize}
\subsection*{Commodity ETPs}
    % Commodities alphabetically sorted.
    \begin{itemize}
        \item Invesco DB Agriculture Fund with ticker DBA which seeks to track changes in the level of the DBIQ Diversified Agriculture Index Excess Return over time. The 11 agricultural commodity futures contracts included in the holdings are corn, soybeans, sugar, coffee, live cattle, lean hogs, cocoa, wheat, Kansas wheat, feeder cattle and cotton. Source: \href{https://www.invesco.com/us-rest/contentdetail?contentId=f919e01e98630410VgnVCM10000046f1bf0aRCRD&dnsName=us}{Invesco Agriculture Fund Fact Sheet as of June 30, 2021}.% \cite{factsheet_dba}.
        
        \item Invesco DB Base Metals Fund with ticker DBB which seeks to track changes in the level of the DBIQ Optimum Yield Industrial Metals Index Excess Return over time. The 3 industrial metals commodity futures contracts included in the holdings are copper, aluminium and zinc. Source: \href{https://www.invesco.com/us-rest/contentdetail?contentId=3919e01e98630410VgnVCM10000046f1bf0aRCRD&dnsName=us}{Invesco DB Base Metals Fund Fact Sheet as of June 30, 2021}.% \cite{factsheet_dbb}.
        
        \item Invesco DB Energy Fund with ticker DBE which seeks to track changes in the level of the DBIQ Optimum Yield Energy Index Excess Return over time. The 5 energy commodity futures contracts included in the holdings are WTI crude, gasoline, NY Harbor ULSD, Brent crude and natural gas. Source: \href{https://www.invesco.com/us-rest/contentdetail?contentId=7519e01e98630410VgnVCM10000046f1bf0aRCRD&dnsName=us}{Invesco DB Energy Fund Fact Sheet as of June 30, 2021}.% \cite{factsheet_dbe}.
        
        \item Invesco DB Precious Metals Fund with ticker DBP which seeks to track changes in the level of the DBIQ Optimum Yield Precious Metals Index Excess Return over time. The 2 precious metals commodity futures contracts included in the holdings are gold and silver. Source: \href{https://www.invesco.com/us-rest/contentdetail?contentId=f619e01e98630410VgnVCM10000046f1bf0aRCRD&dnsName=us}{Invesco DB Precious Metals Fund Fact Sheet as of June 30, 2021}.% \cite{factsheet_dbp}.
    \end{itemize}